---
title: "Intro_to_Rstudio"
author: "Cory"
date: "January 19, 2016"
output: html_document
runtime: shiny
---
These  are just Cory's notes for the first course meeting, with some links

**Download** the folder '1_19_16_Rstudio_Intro' for today's materials [here](https://github.com/cmerow/Stats_Lunch/tree/master/)

# Overview

* Panes
* Open 'Stats_Lunch/1_19_16_Rstudio_Intro/Intro_to_IPMs_Exercises.r'
    + this is just some working code to demo RStudio
* Tabs
* Keystrokes
* files vs. projects
* Nice features
    + syntax highlighting
    + enviroment
    + history
    + buttons galore
* Things I use
    + git
    + knitR/Sweave
    + package handling
    + cluster
* A useful presentation [here](http://dss.princeton.edu/training/RStudio101.pdf)

# Git
* Git and Github
* Github has a GUI you could use, but rstudio is easier...
* Advantages: Track changes, collaborate, share (GUI and command line), track issues, 
* Share: courses, packages, reproducible paper code, all your work?
* Show my account
* Show a package
* Download here: https://git-scm.com/downloads
* Create a repository, if you just [can't wait](https://help.github.com/articles/create-a-repo/)

# R Markdown
* This doc was made with R markdown; open the .Rmd file to see how the code translates to the finished product

* R markdown [cheatsheet](https://www.rstudio.com/wp-content/uploads/2015/02/rmarkdown-cheatsheet.pdf)

```{r}
summary(cars)
```
You can also embed plots, for example:

```{r, echo=FALSE}
plot(cars)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.

* Compare to sweave/Latex
* show IPM book

# Shiny
* A nice example (loads slowly) of [Wallace](http://protea.eeb.uconn.edu:3838/wallace2/)
* someone should lead a week on this!

```{r echo = FALSE}
selectInput("data", "",
 c("co2", "lh"))
```
See a plot:
```{r echo = FALSE}
renderPlot({
 d <- get(input$data)
 plot(d)
})
```

# Package development

* Show meteR
    + github [link](https://github.com/cmerow/meteR)








